%-------------------------
% Cover Letter in LaTeX
% Author : Naveen Pandian
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------------------------
%%%%%%  COVER LETTER STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Naveen Pandian} \\ \vspace{2pt}
    Chennai, Tamil Nadu, India \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-XXXXXXXXXX ~ 
    \href{mailto:npandian515@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{npandian515@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/naveen-pandian-2215732a5/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/naveen-pandian}}  ~
    \href{https://github.com/Neurvinch}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Neurvinch}} ~
    \href{https://x.com/naveenp44368937}{\raisebox{-0.2\height}\faTwitter\ \underline{@naveenp44368937}}
    \vspace{-12pt}
\end{center}

\vspace{0.5in}

\today

\vspace{0.2in}

\textbf{Hiring Manager} \\
\textbf{Company Name} \\
Company Address \\
City, State, Zip Code

\vspace{0.3in}

\textbf{Re: Application for [Job Title] Position}

\vspace{0.2in}

Dear Hiring Manager,

I am writing to express my strong interest in the [Job Title] position at [Company Name], as advertised on [Platform/Referral]. As a Blockchain Full Stack Engineer and 2nd-year dedicated Computer Science student at Jaya Engineering College, I have cultivated a robust skill set in modern web development and distributed systems that aligns perfectly with your team's needs.

Through my experience building full-stack applications like \textbf{WePost} (a social media platform using Next.js and PostgreSQL) and \textbf{KryptoKapital} (a cryptocurrency learning platform), I have demonstrated my ability to deliver scalable, user-centric solutions. I am particularly passionate about the intersection of elegant frontend design and powerful backend architecture, utilizing tools like React, TypeScript, and Node.js to solve complex problems.

My background includes:
\begin{itemize}
    \item Developing responsive, high-performance web applications using the \textbf{Next.js} ecosystem.
    \item Integrating complex state management and real-time features using \textbf{Zustand} and \textbf{Supabase}.
    \item Implementing secure and efficient backend services with PostgreSQL and Redis.
    \item A strong commitment to open-source contributions and continuous learning.
\end{itemize}

I am excited about the opportunity to contribute to [Company Name]'s mission and bring my technical expertise and creative problem-solving skills to your team. I am eager to discuss how my background in full-stack development and blockchain technologies can add value to your projects.

Thank you for considering my application. I look forward to the possibility of discussing this exciting opportunity with you.

Sincerely,

\vspace{0.2in}

\textbf{Naveen Pandian}

\end{document}
